25 years of Social Work Research

### 2015-03-24 dataCleaning.Rmd
Location analysis upgraded and functional

```{r eval=FALSE}
# Read data files
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
countries.csv <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/countries.csv")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
#hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)

@@

@@

```{r locationExtraction2, eval=FALSE}
LO.df2 <- filter(full.df, attributes == "location" | attributes == "abstract" |
                 attributes == "article" | attributes == "keyword")
indx.country <- paste(countries.csv$x, collapse = "|")
library(stringi)
countries.extracted <- na.omit(within(LO.df2, text1<- stri_extract(LO.df2$record, regex=indx.country)))[-2]
country.indexed <- as.numeric(rownames(countries.extracted))
location.ID <- LO.df2$articleID[country.indexed]
detach(package:stringi)
```

@@

location.df <- location.df[location.df$record %in% location.summary.df$country, ]
year.location.df <- left_join(location.df, year.df, by = "articleID") 
colnames(year.location.df) <- c("articleID", "country", "pubYear")
year.location.df <- group_by(year.location.df, country, pubYear) %>%
                    summarise(N = n())

@@

plot.location.withUS <- ggplot(year.location.df, aes(pubYear, N, group = country, colour=country)) + 
    geom_line() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
          title = element_text(size = 10), 
          legend.title=element_blank())  +
    scale_y_continuous(limits = c(0,600)) + 
    xlab("Year") +
    ylab("Articles") +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) + 
    scale_colour_manual(values=cbPalette) +
    ggtitle("Number of Articles by Country and Year")
```

@@

>>>>

```{r eval=FALSE}
# Read data files
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
countries.csv <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/countries.csv")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
#hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)
#countries.csv<-read.csv("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/countries.csv")

@@

#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/appendData.R")
#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/shortArticles.R")
#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/titleMatching.R")
#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/otherDocuments.R")
#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/titleMatching.R")
#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/fewArticles.R")

@@

```{r locationExtraction2, eval=FALSE}
LO.df2 <- filter(full.df, attributes == "abstract" |
                 attributes == "article" | attributes == "keyword")
indx.country <- paste(countries.csv$x, collapse = "[\\s|[[:punct:]]]|")
library(stringi)
countries.extracted <- na.omit(within(LO.df2, text1<- stri_extract(LO.df2$record, opts_fixed=TRUE, regex=indx.country)))[-2]
countries.extracted$text1<-gsub("[[:punct:]]", "", countries.extracted$text1)
countries.extracted$text1<-gsub("^\\s+|\\s+$", "", countries.extracted$text1)

new.countries<-unique(countries.extracted[,c("articleID","text1")])
new.countries<-mutate(new.countries, attributes="location")
new.countries<-select(new.countries, articleID, attributes, record=text1)

loc<-filter(full.df, attributes=="location")
locations<-rbind(loc, new.countries)
locations<-unique(locations[,c("articleID","attributes","record")])
locations<-filter(locations, record!="NA")

#Set of code to address labeling issues related to the United Kingdom

locations$record[locations$record=="Great Britain"]<- "United Kingdom"    #Combines Great Britain and UK records

uk<-filter(locations, record=="United Kingdom")  #creates temp DF with only UK records
ukID<-uk$articleID

#next four blocks of code check to see if the United Kindgom and each country are both listed as a research site and eliminates the UK location record when this was the case.  This means that remaining UK records represent cases of research within the UK in an unspecified country.

scot<-filter(locations, record=="Scotland") 
scotID<-scot$articleID
remove<-ukID%in%scotID
uk.remove<-cbind(uk, remove)
uk.remove<-filter(uk, remove==TRUE)
uk.remove.ID<-uk.remove$articleID
uk<-uk[!(uk$articleID%in%uk.remove.ID),]
ukID<-uk$articleID

eng<-filter(locations, record=="England")  
engID<-eng$articleID 
remove<-ukID%in%engID
uk.remove<-cbind(uk, remove)
uk.remove<-filter(uk, remove==TRUE)
uk.remove.ID<-uk.remove$articleID
uk<-uk[!(uk$articleID%in%uk.remove.ID),]
ukID<-uk$articleID

ni<-filter(locations, record=="Northern Ireland") 
niID<-ni$articleID
remove<-ukID%in%niID
uk.remove<-cbind(uk, remove)
uk.remove<-filter(uk, remove==TRUE)
uk.remove.ID<-uk.remove$articleID
uk<-uk[!(uk$articleID%in%uk.remove.ID),]
ukID<-uk$articleID

wales<-filter(locations, record=="Wales") 
walesID<-wales$articleID
remove<-ukID%in%walesID
uk.remove<-cbind(uk, remove)
uk.remove<-filter(uk, remove==TRUE)
uk.remove.ID<-uk.remove$articleID
uk<-uk[!(uk$articleID%in%uk.remove.ID),]
ukID<-uk$articleID

locations<-filter(locations, record!="United Kingdom")  #removes old UK records
locations<-rbind(locations, uk)

locations$record[locations$record=="US"]<-"United States"
locations$record[locations$record=="Appalachia"]<-"United States"
locations$record[locations$record=="Bosnia"]<-"Bosnia-Herzegovina"
locations$record[locations$record=="Democratic Republic of Congo"]<- "Congo (Brazzaville)"
locations$record[locations$record=="Democratic Republic of the Congo"]<- "Congo (Brazzaville)"
locations$record[locations$record=="Holland"]<- "Netherlands"
locations$record[locations$record=="West Bank"]<-"Palestine"
locations$record[locations$record=="Gaza"]<-"Palestine"
locations$record[locations$record=="Gaza Strip"]<-"Palestine"
locations$record[locations$record=="Trinidad"]<-"Trinidad and Tobago"
locations$record[locations$record=="Gaza"]<-"Palestine"
locations$record[locations$record=="England"]<-"United Kingdom"
locations$record[locations$record=="Northern Ireland"]<-"United Kingdom"
locations$record[locations$record=="Scotland"]<-"United Kingdom"
locations$record[locations$record=="Wales"]<-"United Kingdom"

full.df<-filter(full.df, attributes!="location")
full.df<-rbind(full.df, locations)

detach(package:stringi)
```

@@

location.df.withUS <- location.df[location.df$record %in% location.summary.df$country, ]
year.location.df.withUS <- left_join(location.df.withUS, year.df, by = "articleID") 
colnames(year.location.df.withUS) <- c("articleID", "country", "pubYear")
year.location.df.withUS <- group_by(year.location.df.withUS, country, pubYear) %>%
                    summarise(N = n())

location.summary.df.noUS <- group_by(year.location.df, country) %>%
           summarize(Number = n()) %>%
           arrange(desc(Number)) %>%
           slice(2:7) %>%
           select(country)

location.df.noUS <- location.df[location.df$record %in% location.summary.df.noUS$country, ]
year.location.df.noUS <- left_join(location.df.noUS, year.df, by = "articleID") 
colnames(year.location.df.noUS) <- c("articleID", "country", "pubYear")
year.location.df.noUS <- group_by(year.location.df.noUS, country, pubYear) %>%
                    summarise(N = n())
```

@@

plot.location.withUS <- ggplot(year.location.df.withUS, aes(pubYear, N, group = country, colour=country)) + 
    geom_line() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
          title = element_text(size = 10), 
          legend.title=element_blank())  +
    scale_y_continuous(limits = c(0,700)) + 
    xlab("Year") +
    ylab("Articles") +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) + 
    scale_colour_manual(values=cbPalette) +
    ggtitle("Number of Articles by Country and Year")

plot.location.noUS <- ggplot(year.location.df.noUS, aes(pubYear, N, group = country, colour=country)) + 
    geom_line() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
          title = element_text(size = 10), 
          legend.title=element_blank())  +
    scale_y_continuous(limits = c(0,150)) + 
    xlab("Year") +
    ylab("Articles") +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) + 
    scale_colour_manual(values=cbPalette) +
    ggtitle("Number of Articles by Country and Year, United States Excluded")

@@

```{r}
plot.location.noUS
```
